MSE Scenarios for short and long lived

### 2025-04-15 Scenarios.Rmd
push test from container
updates survey timing to 2024

cod assessment or redfish for these

@@

# get median DOY for each seasonal survey
# from a local surdat pull
# fracyr <- survdat_nobio$survdat |> #file from last May, could update
#   dplyr::mutate(DOY = lubridate::yday(EST_TOWDATE)) |> 
#   dplyr::select(SEASON, DOY) |> dplyr::distinct() |> 
#   dplyr::group_by(SEASON) |> 
#   dplyr::summarise(medDOY = median(DOY), 
#                    fracyrmed = medDOY/365)

>>>>

cod assessment or redfish for these (Brian supplied redfish!)

@@

# get median DOY for each seasonal survey
# from a local surdat pull 
# survdat_nobio <- readRDS(here::here("localhugefiles/survdat_nolength.rds"))
# fracyr <- survdat_nobio$survdat |> #file from April 2025
#   dplyr::mutate(DOY = lubridate::yday(EST_TOWDATE)) |>
#   dplyr::select(SEASON, DOY) |> dplyr::distinct() |>
#   dplyr::group_by(SEASON) |>
#   dplyr::summarise(medDOY = median(DOY, na.rm=T),
#                    fracyrmed = medDOY/365)
# fracyr
# # A tibble: 2 × 3
#   SEASON medDOY fracyrmed
#   <chr>   <dbl>     <dbl>
# 1 FALL     296.     0.812
# 2 SPRING   108.     0.295
